\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2013-12-21 fluB.tex
Adding recap in discussion.
Rehashing results, adding letters to both panels in methodFig.

\begin{figure}[h]
 \centering		
	\includegraphics[width=0.45\textwidth]{figures/TreeFigure2}
	\caption{\textbf{Schematic depiction of method.}
We begin by assigning sequences falling on either side of a specified bifurcation within each segment tree to different lineages.
We then transfer lineage labels from one tree to the same tips in another tree.
Label switches thus indicate reassortment events that combine lineages falling on different sides of the bifurcation specified earlier.
In the example above tip number 6 is determined to be such a reassortant. \tbc{Give this A and B panels.}}
	\label{methodFig}
\end{figure}

@@

\subsection*{Reassortment rates are not significantly different between PB1, PB2 and HA, but reassortment distances can be}
Estimates of normalized SPR distances between pairs of segments (Figure \ref{SPRdistances}) show that there is no evidence of differences in reassortment rates between all segments, based on overlapping 95\% highest posterior density (HPD) intervals.

@@

\subsection*{Rehash streamlined version of results for people who don't read results sections.}

\tbc{Title is approximate.}

>>>>

\begin{figure}[h]
 \centering		
	\includegraphics[width=0.45\textwidth]{figures/TreeFigure2}
	\caption{\textbf{Schematic depiction of method.}
We begin by assigning sequences falling on either side of a specified bifurcation within each segment tree to different lineages.
We then transfer lineage labels from one tree to the same tips in another tree.
Label switches thus indicate reassortment events that combine lineages falling on different sides of the bifurcation specified earlier.
In the example above tip number 6 is determined to be such a reassortant.}
	\label{methodFig}
\end{figure}

@@

\subsection*{Numbers of reassortments are not significantly different between all segments, but reassortment distances can be}
Estimates of normalized SPR distances between pairs of segments (Figure \ref{SPRdistances}) show that there is no evidence of differences in reassortment rates between all segments, based on overlapping 95\% highest posterior density (HPD) intervals.

@@

\subsection*{Rehash streamlined version of results for people who don't read results sections.}
In this paper we have shown that PB1, PB2 and HA segments of influenza B viruses are the only ones that have maintained both a Vic and a Yam lineage (Figure \ref{LineageRatiosOverTime}).
Evidence suggests that this is a result of lack of reassortment between Vic and Yam lineages of these segments (Figure \ref{betweenDiversity}) which have evolved co-assorting amino acid sites detectable as high linkage disequilibrium (\ref{segmentLD}).
We propose that this pattern of non-reassortment is due to the action of selection and not simply biased reassortment.
Figures \ref{SPRdistance} and \ref{deltaTMRCA} show that despite all pairs of segments having the same reassortment frequency, PB1, PB2 and HA segments exhibit much lower reassortment `distances'.
In addition, most strains with mixed-lineage PB1-PB2-HA complexes occured in the early years of the Vic--Yam split, when the two lineages were much more similar at the nucleotide and amino acid levels.
The most recent lineage of influenza B viruses with mixed-lineage PB1-PB2-HA complexes (B/Waikato/6/2005-like) only circulated for 5 months before going extinct.
We suggest that the preservation of two PB1-PB2-HA complex lineages is similar to genomic speciation islands.
If both PB1-PB2-HA complex lineages continue circulating in humans we expect more segments to be recruited to the two complexes, resulting in eventual sympatric speciation of influenza B viruses. 
\tbc{Title is approximate.}
